REVISITING SEMI-CONTINUOUS HIDDEN MARKOV MODELS

### 2011-09-28 misc/papers/icassp12_tied/icassp12.tex
Final edits to paper.
git-svn-id: https://svn.code.sf.net/p/kaldi/code/sandbox/discrim@536 5e6a8d80-dfce-4ca6-a32a-6e07a63d50c8

In the experiments we report here we have not been able to match the performance of
a standard diagonal GMM based system using a traditional semi-continuous system;
however, using a two-level tree and multiple codebooks similar to~\cite{prasad2004t2b},
we were able to get better performance than a traditional system (although not
as good as SGMMs).  For both traditional and multiple-codebook configurations,
we saw better results with full-covariance codebook Gaussians than with diagonal.
We investigated smoothing the statistics for weight estimation using the decision
tree, and saw only modest improvements.
We note that the software used to do the experiments is part of the {\sc Kaldi} speech
recognition toolkit~\cite{povey2011tks} and is freely available for download, along with the
example scripts to reproduce these results.

@@

In this article, we compared continuous and SGMM models with
two types of semi-continuous hidden Markov models, one using a single codebook 
and the other using multiple codebooks based on a two-level phonetic decision tree,
similar to~\cite{prasad2004t2b}.
Using the single-codebook system we were not able to obtain competitive
results, but using a multiple-codebook system 
we were able to get better results than a traditional system.  Interestingly,
for both the single-codebook or multiple-codebook systems, we saw better
results with full rather than diagonal covariances.

@@

% Korbinian: We might need that ;)
\footnotesize
\bibliographystyle{IEEEbib}
\bibliography{refs-eig,refs}

>>>>

In the experiments we report here we have not been able to match the performance of
a standard diagonal GMM based system using a traditional semi-continuous system;
however, using a two-level tree and multiple codebooks similar to~\cite{prasad2004t2b},
in one setup we were able to get better performance than a traditional system (although not
as good as SGMMs).  For both traditional and multiple-codebook configurations,
we saw better results with full-covariance codebook Gaussians than with diagonal.
We investigated smoothing the statistics for weight estimation using the decision
tree, and saw only modest improvements.
We note that the software used to do the experiments is part of the {\sc Kaldi} speech
recognition toolkit~\cite{povey2011tks} and is freely available for download, along with the
example scripts to reproduce these results.

@@

In this article, we compared continuous and SGMM models with
two types of semi-continuous hidden Markov models, one using a single codebook 
and the other using multiple codebooks based on a two-level phonetic decision tree,
similar to~\cite{prasad2004t2b}.
Using the single-codebook system we were not able to obtain competitive
results, but using a multiple-codebook system 
we were able to get better results than a traditional system, for one
database (RM).  Interestingly,
for both the single-codebook or multiple-codebook systems, we saw better
results with full rather than diagonal covariances.

@@

% Korbinian: We might need that ;)
%\footnotesize

\bibliographystyle{IEEEbib}
\bibliography{refs-eig,refs}
